\documentclass[mathNotesPreamble]{subfiles}
\begin{document}
%\relscale{1.4}
\section{4.5: Optimization Problems}
\textit{Note: } Please note that these `word problems' are different from the related rates problems that we did in section 3.11.
\vspace*{\stretch{0.35}}

\begin{thmBox*}[Guidelines for Optimization Problems]
  \begin{enumerate}
    \item Read the problem and identify variables with a diagram. Only put numbers on the diagram if they are constant.
    \item Express the function that will be optimized.
    \item Identify the constraint(s). Use the constraint(s) to eliminate/rewrite all but the single independent variable of the objective function.
    \item Use derivatives to find the absolute max/min of the objective function.
    
      \textbf{Make sure you are finding the correct extrema!}
      \begin{itemize}
        \item First derivative test ($f'(x)$ changes signs at $x=c$)
        \item Second derivative test ($f'(c)<0$ (neg) means $f(c)$ is a max).
        \item Evaluate at endpoints and critical points.
      \end{itemize}
    \item Summarize your result in a sentence.
  \end{enumerate}
\end{thmBox*}
\vspace*{\stretch{1}}
\pagebreak

\begin{enumerate}[itemsep=\stretch{1}]
  \item 
    A farmer has 2400 feet of fencing and wants to fence off a rectangular field that borders a straight river. He decides not to fence along the river. What are the dimensions of the field that has the largest area?
    \begin{enumerate}[label=, itemsep=\stretch{1}]
      \item Draw a diagram. Define your variables.
      \item Express your constraints and the variable that needs optimizing.
      \item Find the local maximum.
      \item Verify the critical point is the absolute maximum.
      \item State your answer ensuring that you are answering the question asked.
    \end{enumerate}
    \vspace*{\stretch{1}}
    \pagebreak
  \item 
    Show among all rectangles with an 8 meter perimeter, the one with the largest area is a square.
  \item 
    Find $x$ and $y$ such that $xy=50$ but $x+y$ is minimal. $(x>0, y>0)$
    \vspace*{\stretch{1}}
    \pagebreak
  \item 
    A box with a square base and an open top must have a volume of $32,000\,cm^{3}$. Find the dimensions of the box that minimizes the amount of material used.
    \pagebreak
  \item 
    If $y=2x-89$, what is the minimum value of the product $xy$?
    \pagebreak
  \item
    A farmer has 900 meters of fencing. The fencing is to be used to enclose a rectangular field and to divide it in half. Find the dimensions of the field that has maximum area.
    \pagebreak
  \item 
    A rectangle is constructed with its base on the $x$-axis and two of its vertices on the parabola $y=48-x^2$. What are the dimensions of the rectangle with the maximum area? What is the area?
    \pagebreak
  \item 
    Find the point on the curve $y=\sqrt x$ that is closest to the point $(3,0)$. 
    \pagebreak
  \item 
    A cylindrical can is to be made to hold $1\,L$ ($1000\,cm^3$) of oil. Find the dimensions of the can that will minimize the cost of the metal to manufacture the can.
    \pagebreak
  \item 
    A man launches his boat from point $A$ on a bank of a straight river, $3\, km$ wide, and wants to reach point $B$, $8\, km$ downstream on the opposite bank, as quickly as possible.  He could row his boat directly across the river to point $C$ and then run to $B$, or he could row directly to $B$, or he could row to some point between point $C$ and point $B$ and then run to $B$.  If he can row $6\, km/h$ and run $8\, km/h$, where should he land to reach $B$ as soon as possible?  (\textit{Assume that the speed of the water is negligible compared with the speed at which the man rows.})
    \pagebreak
  \item 
    The top and bottom margins of a poster are each $6\,cm$ and the side margins are each $4\,cm$.  If the area of printed material on the poster is fixed at $384\,cm^2$, find the dimensions of the poster with the smallest area.
    \pagebreak
  \item 
    A cabin is located $2\, km$ directly into the woods from a mailbox on a straight road. A store is located on the road $5\,km$ from the mailbox.  A woman wished to walk from the cabin to the store. She can walk $3\, km/h$ through the woods and $4\, km/h$ along the road. Find the point on the road toward which she would walk in order to minimize the total time for her walk.
    \pagebreak
  \item 
    We want to construct a box whose base length is 3 times the base width. The material used to build the top and bottom cost \$$10/ft^2$ and the material used to build the sides costs \$$6/ft^2$. If the box must have a volume of $50\,ft^3$ determine the dimensions that will minimize the cost to build the box.
    \pagebreak
  \item 
    An open-top rectangular box is constructed from a $10\, in.$ by $16\,in.$ piece of cardboard by cutting squares of equal side length from the corners and folding up the sides. Find the dimensions of the box of largest volume and the maximum volume.
    \pagebreak
  \item 
    Find the dimensions of the rectangle of largest area that can be inscribed in a circle of radius $\sqrt2\, cm$.
    \pagebreak
  \item 
    A rectangle is constructed with one side on the positive $x$-axis, one side on the positive $y$-axis, and the vertex opposite the origin on the line $y=10-2x$.  What dimensions maximize the area of the rectangle?  What is the maximum area?
    \pagebreak
  \item 
     A Norman window has the shape of a rectangle surmounted by a semi-circle. (Thus, the diameter of the semi-circle is equal to the width of the rectangle.) If the perimeter of the window is $20\, ft$, find the dimensions of the window so that the greatest possible amount of light is admitted.
\end{enumerate}
\pagebreak  
\end{document}
